Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/simulation.tex
Move figures around and use subfigures more.

>>>>

\begin{figure}
%\centering
\begin{subfigure}[b]{0.25\textwidth}
\centering
\includegraphics[width=1.5in]{../figs/synthetic/mat.pdf}
\end{subfigure}
~
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=2in]{../figs/synthetic/counts.pdf}
\end{subfigure}
~
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=2.5in]{../figs/synthetic/params-estimates.pdf}
\end{subfigure}
\caption{Illustration of 2000 simulated events, as described in text. Left: Counts of each dyad. Center: Boxplot of distribution of participation counts across dyads.  The top left shows an increased propensity for reciprocity within cluster 1; bottom right shows more AB-AY events within cluster 2.  Right: Parameters (in red) and posterior credible intervals (in black).}
\label{fig:syncounts}
\end{figure}
